Fig2

### 2020-02-21 analysis/figure-2.Rmd
more candidate genes, better parental lists

candidategenes <- c("OXT", "AVP", "GNRH1",  "AR", "POMC", "AGRP",
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9", 
                    "ESR1","ESR2", "LBH", "CDK1", "BRCA1",
                    "PTEN", "CREBBP", "FOS", "JUN", "EGR1",
                     "BDNF", "GRM2",
                    "KCNJ5", "CISH", "PTGER3", "CEBPD", "ZBTB16")

table1 <- allDEG %>%
  filter(gene %in% candidategenes,
         comparison != "group_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, bldg_lay, lay_inc.d3, inc.d3_inc.d9,
        inc.d9_inc.d17,inc.d17_hatch, hatch_n5, n5_n9)  %>%
  arrange( tissue, sex)
table1

write_csv(table1, "../results/table1.csv")

suppletable1 <- allDEG %>%
  filter(comparison != "control_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  arrange( tissue, sex)

@@

write_csv(table1, "../results/suppletable1.csv")

>>>>

candidategenes <- c("OXT", "AVP", "GNRH1", "GNRHR", "CGNRH-R",
                    "AR", "POMC", "AGRP", 
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2","VIP",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9", 
                    "ESR1","ESR2", "LBH", "CDK1", "BRCA1",
                    "PTEN", "CREBBP", "FOS", "JUN", "EGR1",
                     "BDNF", "GRM2","GRIA1",
                    "KCNJ5", "CISH", "PTGER3", "CEBPD", "ZBTB16", 
                    "DIO3", "DIO2", "DIO1")

table1 <- allDEG %>%
  filter(gene %in% candidategenes,
         comparison != "control_bldg") %>%
    arrange(gene) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, bldg_lay, lay_inc.d3, inc.d3_inc.d9,
        inc.d9_inc.d17,inc.d17_hatch, hatch_n5, n5_n9)  %>%
  arrange( tissue, sex)
table1

table2 <- allDEG2 %>%
  filter(gene %in% candidategenes) %>%
  arrange(gene) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  arrange( tissue, sex)
table2

write_csv(table1, "../results/table1.csv")
write_csv(table2, "../results/table2.csv")
```

## supplemental tables, all DEGS

```{r}

suppletable1 <- allDEG %>%
  filter(comparison != "control_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  arrange( tissue, sex, direction, gene)
head(suppletable1)

@@

suppletable2 <- allDEG2 %>%
  filter(comparison != "control_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  arrange( tissue, sex, direction, gene)
head(suppletable2)

write_csv(suppletable1, "../results/suppletable1.csv")

write_csv(suppletable2, "../results/suppletable2.csv")

head(allDEG) 
```

## female pit, parental/repro only, not PRL

```{r}
allDEGslim <- allDEG %>% filter(comparison != "control_bldg")

femalepitPRL <- allDEG2 %>% filter(sex == "female", tissue == "pituitary") %>%
  filter(comparison != "eggs vs. chicks") %>% arrange(gene) %>% pull(gene)

femalepitparental <- allDEGslim %>% 
  filter(!gene %in% femalepitPRL,
         sex == "female", tissue == "pituitary") %>%
  arrange(gene, sex, tissue, comparison, direction) %>%
  distinct(gene) %>% pull(gene)
femalepitparental

malepitPRL <- allDEG2 %>% filter(sex == "male", tissue == "pituitary") %>%
  filter(comparison != "eggs vs. chicks") %>% arrange(gene) %>% pull(gene)

malepitparental <- allDEGslim %>% 
  filter(!gene %in% malepitPRL,
         sex == "male", tissue == "pituitary") %>%
  arrange(gene, sex, tissue, comparison, direction) %>%
  distinct(gene) %>% pull(gene)
malepitparental
